Hybrid platforms and bargaining power

### 2024-01-12 src/paper/application.tex
Rewrite conclusions

This paper has introduced a new model of hybrid platforms in which bargaining between the platform and the entrant firms plays a key role.
It has been demonstrated that platforms operating in hybrid mode can have serious consequences in such an environment.
In particular, when a platform has a large number of its own products, then its bargaining power is also higher compared to the fringe entrants.
This, in certain situations, such as the one described in this paper, this can lead to fewer fringe firms entering the market, reduced product variety, and ultimately, lower consumer welfare.

In addition to the specific platform model, this paper also provides a simple, tractable, yet quite general framework in which one can study the effects of bargaining between one large and a continuum of small players.
Such environments might, in addition to platforms, include upstream-downstream settings with one upstream supplier, or franchises with one franchisor and a continuum of franchisees, or wage bargaining.
The quite general results of this paper give some intuition on what happens in such settings, without needing to delve into the details of a specific model.
This also highlights certain similarities between those markets.
Furthermore, many of the results from this paper can be applied in a plug-and-play fashion to other models of large-player-small-player interactions.

There is a number of avenues for future research in this direction.
First, I suspect that many of the assumptions made in section \cref{sec:example} can be relaxed, and one can still obtain similar results.
An additional step I am planning to take is to endogenize the number of the platform's products, and the parameters of the profit sharing (bargaining rule).
The latter would provide important insights into what kind of demand structures might lead to the evolution of hybrid platforms.

I also hope that others will find this framework useful in their own research, and incorporate it in more complex and more applied models.
In general, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power, and modeling the bargaining process in detail, and might be a good fit for a number of different economic applications.

>>>>

This paper introduces a new model of hybrid platforms in which bargaining between the platform and the entrant firms plays a key role.
It highlights the importance of a so far overlooked aspect of platforms having their own products: the fact that it increases their bargaining power compared to other players'.
As a result, even in the absence of other frictions, hybrid platforms might have detrimental effects on fringe entry.
This, in certain situations, such as the one described in this paper, this can lead to fewer fringe reduced product variety, and ultimately, lower consumer welfare.

The contributions of this paper can be broken down into two categories.
First, a simple, but quite general model of bargaining between one indispensable player and a continuum of potential market entrants is introduced.
This model is applicable beyond the platform setting, and can describe other markets, such as upstream-downstream relations, or franchising, as well.
The quite general results obtained from this model also highlight the similarities between those markets.
Furthermore, many of the results from this paper can be applied in a plug-and-play fashion to other models of large-player-small-player interactions.

The second set of contributions pertains to applying the aforementioned model to a setting with a hybrid platform.
The demand structure is similar to the one in \textcite{anderson2021hybrid}, and the results convey the same general message: hybrid platforms can have detrimental welfare effects.
However, the mechanism behind this result is quite different.
This paper relies on the change in bargaing power, and shows that even in the case of lump-sum entry fees, hybrid platforms can be problematic from a welfare perspective.
An extension of the main model also highlight the importance of the assumptions on who is participating in the bargaining process.

There is a number of avenues for future research in this direction.
First, although the results provide some suggestions about what endogenizing the number of the platform's products might entail, a more formal analysis is needed for a more complete picture.
Second, applying the same bargaining framework, but using a different demand structure (e.g. CES utility) for microfounding the profit functions would have important implications for the robustness of the results.
Finally, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power, and modeling the bargaining process in detail, and some of the main ideas in this paper might be a good fit for different settings and and more applied models.
